Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-22 paper.tex
Clean up acknowledgements

\vspace{6pt}
\acknowledgments{\textbf{Acknowledgments:} The authors would like to acknowledge funding through a National Science
Foundation CAREER %please define
 award (PI %please define
  Wosnik, NSF-CBET%please define
 1150797, program manager 
Gregory L. Rorrer), a grant through the \linebreak Leslie S. Hubbard Marine Program
Endowment to purchase acoustic flow measurement instrumentation and a grant for
laboratory infrastructure upgrades through the U.S. Department of Energy.}

>>>>

% Note for acknowledgements: CAREER is a type of award from the National Science
% Foundation, and is not an acronym.

\vspace{6pt} \acknowledgments{\textbf{Acknowledgments:} The authors would like
    to acknowledge funding through a National Science Foundation CAREER award
    (principal investigator Martin Wosnik, NSF 1150797, Energy for Sustainability,
    program manager Gregory L. Rorrer), a grant through the Leslie S. Hubbard Marine
    Program Endowment to purchase acoustic flow measurement instrumentation, and a
    grant for laboratory infrastructure upgrades through the U.S. Department of
    Energy.}
